\name{}: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-04-09 paper/main.tex
.

>>>>

Combining bottom-up and top-down approaches in a single model can
follow different strategies. Graph neural networks are a natural way
to represent interactions between proteins, and interaction networks
are used widely to determine indirect effects of molecular changes
\cite{}.

Graph neural networks \cite{} have the ability to
represent interaction networks
